---
title: "p8105_hw5_wc2788"
author: "Wen Cheng"
date: "11/18/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
```

## Problem 1
Import and clean data
```{r}
homicide_df = read.csv("homicide-data.csv", na = c("","Unknown")) %>%
  mutate(city_state = str_c(city, state), #create a city_state variable
         resolution = case_when(
           disposition == "Closed without arrest" ~ "unsolved",
           disposition == "Open/No arrest" ~ "unsolved",
           disposition == "Closed by arrest" ~ "solved" #classify solved and unsolved
         )) %>%
  relocate(city_state) %>%
  filter(city_state != "TulsaAL")
```

For city Baltimore, MD
```{r}
baltimore_df = homicide_df %>%
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
  baltimore_df %>%
  summarize(unsolved = sum(resolution == "unsolved"),
            n = n())

baltimore_test = 
  prop.test(x = baltimore_summary %>% pull(unsolved),
            n = baltimore_summary %>% pull(n))

baltimore_test %>%
  broom::tidy()
```

Run prop.test for each of the cities in the dataset
```{r}
prop_test_function = function(city_df) {
  
  city_summary = 
  city_df %>%
  summarize(unsolved = sum(resolution == "unsolved"),
            n = n())

  city_test = 
    prop.test(x = city_summary %>% pull(unsolved),
              n = city_summary %>% pull(n))

  return(city_test)
  
}

homicide_df %>%
  filter(city_state == "AlbuquerqueNM") %>%
  prop_test_function()
```

```{r}
results_df = 
  homicide_df %>%
  nest(data = uid:resolution) %>%
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>%
  select(city_state, tidy_results) %>%
  unnest(tidy_results) %>%
  select(city_state, estimate, starts_with("conf"))

results_df
```

create a plot showing estimates and confidence intervals
```{r}
results_df %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
  
```

```{r}
homicide_df %>%
  group_by(city_state) %>%
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  ) %>%
  mutate(
    test_results = map2(unsolved, n, prop.test),
    tidy_results = map(test_results, broom::tidy)
  ) %>%
  select(city_state, tidy_results) %>%
  unnest(tidy_results) %>%
  select(city_state, estimate, starts_with("conf"))
```

## Problem 2

Create a tidy dataframe containing data from all participants
```{r}
study_df = 
# a dataframe containing all file names
  tibble(
    files = list.files(path = "data", pattern = ".csv", full.names = FALSE)
    ) %>%
  mutate(
    data = map(files, ~read.csv(str_c("data/", .x)))) %>% #iterate over file names
  unnest(data) %>% 

# clean data
  janitor::clean_names() %>% 
  separate(files, c('arm', 'subject_id'), "_") %>% #separate file names into arm and subject ID
  pivot_longer(
    week_1 : week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observation"
  ) %>% #weekly observations are “tidy”
  mutate(
    arm = recode(arm, "con" = "Control", "exp" = "Experiment"),
    subject_id = str_replace(subject_id, "\\.csv", "") #looks nicer
    )

study_df
```

Make a spaghetti plot
```{r}
study_df %>% 
  ggplot(aes(x = week, 
             y = observation, 
             group = subject_id, 
             color = subject_id)
         ) + 
  geom_point() +
  geom_line() +
  facet_grid( ~ arm) +
  labs(
    title = "Observations on each subject over time",
    x = "Week",
    y = "Observation"
  ) 
```
From the spaghetti plot, we can see the observation value in control arm are stay same(not obviously increasing or decreasing) in 8 weeks, the observation value in experiment arm are increasing over time.

## Problem 3
Load the iris dataset
```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
view(iris_with_missing)
```

Write a function replaces missing values
```{r}
fill = function(x){
  if(is.numeric(x)){
    x = replace_na(x, mean(x, na.rm = TRUE))
  }
  if(is.character(x)){
    x = replace_na(x, "virginica")
  }
  return(x)
}
```

Apply function to iris_with_missing
```{r}
map_df(iris_with_missing, fill)
```